Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism

### 2022-03-03 papers/03 journal final/journal_v16.tex
update v16

%\smallskip
\paragraph*{Dispatchable units}
The objective function of a dispatchable unit, denoted by $f_{i}^{\mathrm{di}}: \mathbb{R}^{H} \to \mathbb{R}$, is typically a convex quadratic function   \cite{atzeni2013,hans2018,sorin2019}, e.g. 
\begin{equation}
f_{i}^{\mathrm{di}}(p_{i}^{\mathrm{di}}) = \|p_{i}^{\mathrm{di}}\|_{Q_i^{\mathrm{di}}}^2+ {(c_i^\mathrm{di})}^\top p_{i}^{\mathrm{di}}, \label{eq:f_dg}
\end{equation}
where $Q_i^{\mathrm{di}}\succcurlyeq0$ and $c_i^{\mathrm{di}}$ are constants.
Furthermore, the power generation $p_{i}^{\mathrm{di}}$ is limited by 
\begin{equation}
\begin{aligned}
\underline{p}_{i}^{\mathrm{di}}\1_{H} \leq p_{i}^{\mathrm{di}} &\leq \overline{p}_{i}^{\mathrm{di}}\1_{H}, \quad& &\forall i\in\mathcal{N}^{\mathrm{di}},\\
p_{i}^{\mathrm{di}} &= 0, \quad& &\forall i\notin\mathcal{N}^{\mathrm{di}},
\end{aligned}
\label{eq:p_dg_bound}	
\end{equation}
where $\overline{p}_{i}^{\mathrm{di}} > \underline{p}_{i}^{\mathrm{di}}\ge 0$ denote maximum and minimum total power production of the dispatchable generation unit, and $\mathcal{N}^{\mathrm{di}}\subseteq\mathcal{N}$ the subset of agents that own dispatchable units.

%\smallskip
\paragraph*{Storage units} 
Each prosumer might also minimize the usage of its storage units, for instance, in order to reduce its degradation. The corresponding cost function is denoted by $f_{i}^{\mathrm{st}}:\mathbb{R}^{H} \to \mathbb{R}$, defined as in \cite{hans2018}:
\begin{equation}
f_{i}^{\mathrm{st}}(p_{i}^{\mathrm{ch}}, p_{i}^{\mathrm{ds}})= \|p_{i}^{\mathrm{ch}}\|_{Q_i^{\mathrm{st}}}^2 + \|p_{i}^{\mathrm{ds}}\|_{Q_i^{\mathrm{st}}}^2, \label{eq:f_st}
\end{equation}
where $Q_i^{\mathrm{st}}\succcurlyeq0$. {The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics \cite{atzeni2013,zhong2019online}}
%
\begin{equation}
	\begin{aligned}
	%	\left.
	%	\begin{array}{c}
			x_{i,h+1} &=\eta_i^{\mathrm{st}} x_{i,h} +\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\frac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}), %\forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\[.2em]
		\\
			\underline{x}_i &\leq x_{i,h+1} \leq \overline{x}_i,  \qquad \forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\%[.2em]
			{p}_{i}^{\mathrm{ch}} &\in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],  \quad  \forall i \in \mc N^{\mathrm{st}},
	%	\end{array}
	%	\hspace{-5pt} \right\} & \begin{matrix}
	%	\end{matrix} 
	\\
		p_{i}^{\mathrm{ch}} &= 0, \ \ p_{i}^{\mathrm{ds}}= 0,\qquad \qquad \quad \  \forall i \notin \mc N^{\mathrm{st}},
	\end{aligned}
	\label{eq:x}
\end{equation}
where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation. However, the optimal strategies that they produce satisfies the constraint that charging and discharging must be mutually exclusive (see footnote 1 in \cite{atzeni2013}). From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
, {$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with 
$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively. Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas ${\overline p^{\mathrm{ch}}_i} \geq 0$ and ${\overline p^{\mathrm{ds}}_i} \geq 0$ denote the maximum charging and discharging power of the storage unit. Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.

@@

\item a (dual) variable $\mu_{y}^{\text{pb}}$ for each bus $y \in \mc B$, associated with the power balance constraint on bus $y$ \eqref{eq:p_bal_p}.
\end{itemize}
From an economic perspective, these variables can be interpreted as extra marginal losses imposed to the prosumers for the grid usage. From a control-theoretic perspective, they can be interpreted as states of discrete-time integrators driven by the violation of the network operational constraints \eqref{eq:Cconstr_def}.
}
%
\begin{figure}[t]
\centering
\includegraphics[width=.28\textwidth]{figures/37bus_sys_f6}
\smallskip
\caption{{Information flow in Algorithm 1.}}
\label{fig:IFC}
\end{figure}%
%
\begin{figure}[t]
{
\begin{minipage}{\columnwidth}
\hrule
\smallskip
\textsc{Algorithm 1}. Coordinated P2P Market Clearing
\smallskip
\hrule 
\smallskip
\text{Initialization}: For all prosumers $i \in \mc N$: set $\mu^{\text{tr}}_{(i,j)}(-1) = 0$, $\forall j \in \mc N_i$. DNO: set $\lambda^{\text{mg}}(0)\!=\!0$, $\mu^{\text{tg}}(0) \!=\! 0$, $\mu_y^{\text{pb}}(0)\! = \!0$, $\forall y \!\in\! \mc B$.

@@

Some of the default cost parameters are set as in \cite{atzeni2013}, i.e., $Q_i^{\mathrm{di}}=0$, $c_i^{\mathrm{di}}=0.045\,  \text{\euro/kW}$, for all $i \in \mc N^{\mathrm{di}}$, $Q_i^{\mathrm{st}}=0$, $c_i^{\mathrm{st}}=0$, for all $i \in \mc N^{\mathrm{st}}$, and $d_h^{\mathrm{mg}}=0.1624/b_h \, \text{\euro/kW}$, whereas the trading cost parameters $c_{(i,j)}^{\mathrm{tr}}=0.08 \,  \text{\euro/kW}$, for all $(i,j) \in \mc E$, and $c^{\mathrm{ta}}=0.01 \,  \text{\euro/kW}$. The parameter $c_{(i,j)}^{\mathrm{tr}}$ is set larger than $c_i^{\mathrm{di}}$ to encourage trading between prosumers with and without dispatchable units, but is smaller than the average unit-price of importing power from the main grid. Note that, in some simulations, we vary these cost parameters. 
%
%
\subsection{Achieving operationally-safe solutions}
In the first simulation study, we compare the solutions obtained from solving a P2P market model with and without capacity constraints \eqref{eq:line_cap}. We specifically create an extreme case with $25$ prosumers, where the load of  prosumer $10$ (see Figure \ref{fig:simD_safe}) is very high. We solve both market designs using Algorithm~1. Figure \ref{fig:simD_safe} shows the resulting power-line saturations between busses for both designs. 
%
Some equilibrium solutions of the P2P market cause overcapacity in some lines when capacity constraints \eqref{eq:line_cap} are not taken into account in the model, as illustrated in Figure \ref{fig:simD_safe}~(b).
\begin{figure}[t]
	\centering
	\begin{subfigure}[t]{0.23\textwidth}
		\centering
		\includegraphics[scale=0.9]{figures/simD_safe1}
		\caption{With physical constraints}
	\end{subfigure}%
	~ 
	\begin{subfigure}[t]{0.27\textwidth}
		\centering
		\includegraphics[scale=0.9]{figures/simD_fail2}
		\caption{Without physical constraints}
	\end{subfigure}
	\caption{Power line capacities of the physical network. The solutions of the P2P market might cause overcapacity in some lines of the physical network when capacity constraints \eqref{eq:line_cap} are not taken into account.}
	\label{fig:simD_safe}
\end{figure}

@@

%	
\begin{figure}[htbp]
	\centering
	\includegraphics[width=.9\linewidth]{figures/b0a.eps}
	\caption{Total cost improvement (\euro) of each prosumer by trading ($c_{(i,j)}^{\mathrm{tr}}=0.08\text{\euro/kW}$).
	}
	\label{fig:simC_cost}
\end{figure}
%
\begin{figure}[htbp]
	\centering
	\includegraphics[width=.9\linewidth]{figures/b1a.eps}
	\caption{Aggregated P2P trading for different cost coefficients ($c_{(i,j)}^{\mathrm{tr}}$ in \euro/kW).
	}
	\label{fig:simC_ctr}
\end{figure}
%
\begin{figure}[t!]
	\centering
	\includegraphics[width=.9\linewidth]{figures/b2a.eps}
	\caption{Aggregated P2P trading for different penalty coefficients ($c^{\mathrm{ta}}$ in \euro/kW).
	}
	\label{fig:simC_pen}
\end{figure}
%
Then, we evaluate the sensitivity of the total traded power with respect to the trading cost parameter $c_{(i,j)}^{\mathrm{tr}}$ and the trading tariff, $c^{\mathrm{ta}}$. Figure \ref{fig:simC_ctr} shows that   $c_{(i,j)}^{\mathrm{tr}}$ must be set appropriately to maximize trading among prosumers. In other words, when $c_{(i,j)}^{\mathrm{tr}}$ is either too high or low, trading is less attractive. 
On the other hand, the higher the tariff is, the less power is traded, as shown in Figure \ref{fig:simC_pen}. Therefore, the DNO may adjust this tariff to encourage or discourage trading in the network. Discouraging trading might be needed when the capacity of the network is close to its limit.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.9\linewidth]{figures/simB_0402_pt1_v3a}
	\caption{	Incorporating storage units causes a peak-shaving effect on the sum of the total power imported from the main grid and the power locally generated.}
	\label{fig:sim_B1}
\end{figure}
\begin{figure}[t]
	\centering 
	%\hspace{-17pt}
	\includegraphics[width=0.9\linewidth]{figures/simB_0402_pt2_v4a}
	\caption{Aggregated P2P trading in scenarios (a) and (b).
	}
	\label{fig:sim_B2}
\end{figure}  
\begin{figure}[t]
	\centering 
	%\hspace{-17pt}
	\includegraphics[width=0.9\linewidth]{figures/simB_0402_pt3_v2a}
	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices.
	}
	\label{fig:sim_B3}
\end{figure}  
\iffalse 
\begin{figure}[!t]
	\centering
	\includegraphics[width=0.9\linewidth]{figures/simC_37_v2.eps}
	\caption{\textcolor{red}{[OLD]} Peak shaving effect with different per-unit cost of using storage.
	}
	\label{fig:simC}
\end{figure}
\fi 
%\clearpage

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.9\linewidth]{figures/simEF2.eps}
	\caption{Total number of iterations for convergence of Alg. 1 vs number of prosumers (top) and the connectivity level (the number of trading links) (bottom). {The average computation times of the inner loops, i.e., Algs.~2 and 3, obtained on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory, are 74.5 ms and 1.13 s, respectively.} 
	}
	\label{fig:simE}
\end{figure}

>>>>

\smallskip
\paragraph*{Dispatchable units}
The objective function of a dispatchable unit, denoted by $f_{i}^{\mathrm{di}}: \mathbb{R}^{H} \to \mathbb{R}$, is typically a convex quadratic function   \cite{atzeni2013,hans2018,sorin2019}, e.g. 
\begin{equation}
f_{i}^{\mathrm{di}}(p_{i}^{\mathrm{di}}) = \|p_{i}^{\mathrm{di}}\|_{Q_i^{\mathrm{di}}}^2+ {(c_i^\mathrm{di})}^\top p_{i}^{\mathrm{di}}, \label{eq:f_dg}
\end{equation}
where $Q_i^{\mathrm{di}}\succcurlyeq0$ and $c_i^{\mathrm{di}}$ are constants.
Furthermore, the power generation $p_{i}^{\mathrm{di}}$ is limited by 
\begin{equation}
\begin{aligned}
\underline{p}_{i}^{\mathrm{di}}\1_{H} \leq p_{i}^{\mathrm{di}} &\leq \overline{p}_{i}^{\mathrm{di}}\1_{H}, \quad& &\forall i\in\mathcal{N}^{\mathrm{di}},\\
p_{i}^{\mathrm{di}} &= 0, \quad& &\forall i\notin\mathcal{N}^{\mathrm{di}},
\end{aligned}
\label{eq:p_dg_bound}	
\end{equation}
where $\overline{p}_{i}^{\mathrm{di}} > \underline{p}_{i}^{\mathrm{di}}\ge 0$ denote maximum and minimum total power production of the dispatchable generation unit, and $\mathcal{N}^{\mathrm{di}}\subseteq\mathcal{N}$ the subset of agents that own dispatchable units.

%\smallskip
\paragraph*{Storage units} 
Each prosumer might also minimize the usage of its storage units, for instance, in order to reduce its degradation. The corresponding cost function is denoted by $f_{i}^{\mathrm{st}}:\mathbb{R}^{H} \to \mathbb{R}$, defined as in \cite{hans2018}:
\begin{equation}
f_{i}^{\mathrm{st}}(p_{i}^{\mathrm{ch}}, p_{i}^{\mathrm{ds}})= \|p_{i}^{\mathrm{ch}}\|_{Q_i^{\mathrm{st}}}^2 + \|p_{i}^{\mathrm{ds}}\|_{Q_i^{\mathrm{st}}}^2, \label{eq:f_st}
\end{equation}
where $Q_i^{\mathrm{st}}\succcurlyeq0$. {The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics \cite{atzeni2013,zhong2019online}}
%
\begin{equation}
	\begin{aligned}
	%	\left.
	%	\begin{array}{c}
			x_{i,h+1} &=\eta_i^{\mathrm{st}} x_{i,h} +\tfrac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\tfrac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}), %\forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\[.2em]
		\\
			\underline{x}_i &\leq x_{i,h+1} \leq \overline{x}_i,  \qquad \forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\%[.2em]
			{p}_{i}^{\mathrm{ch}} &\in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],  \quad  \forall i \in \mc N^{\mathrm{st}},
	%	\end{array}
	%	\hspace{-5pt} \right\} & \begin{matrix}
	%	\end{matrix} 
	\\
		p_{i}^{\mathrm{ch}} &= 0, \ \ p_{i}^{\mathrm{ds}}= 0,\qquad \qquad \quad \  \forall i \notin \mc N^{\mathrm{st}},
	\end{aligned}
	\label{eq:x}
\end{equation}
where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation. However, the optimal strategies that they produce satisfies the constraint that charging and discharging must be mutually exclusive (see footnote 1 in \cite{atzeni2013}). From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
, {$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with 
$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively. Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas ${\overline p^{\mathrm{ch}}_i} \geq 0$ and ${\overline p^{\mathrm{ds}}_i} \geq 0$ denote the maximum charging and discharging power of the storage unit. Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.

@@

\item a (dual) variable $\mu_{y}^{\text{pb}}$ for each bus $y \in \mc B$, associated with the power balance constraint on bus $y$ \eqref{eq:p_bal_p}.
\end{itemize}
From an economic perspective, these variables can be interpreted as extra marginal losses imposed to the prosumers for the grid usage. From a control-theoretic perspective, they can be interpreted as states of discrete-time integrators driven by the violation of the network operational constraints \eqref{eq:Cconstr_def}.
}
%
\begin{figure}[t]
\centering
\includegraphics[width=.29\textwidth]{figures/37bus_sys_f6}
\smallskip
\caption{{Information flow in Algorithm 1.}}
\label{fig:IFC}
\end{figure}%
%
\begin{figure}[t]
{
\begin{minipage}{\columnwidth}
\hrule
\smallskip
\textsc{Algorithm 1}. Coordinated P2P Market Clearing
\smallskip
\hrule 
\smallskip
\text{Initialization}: For all prosumers $i \in \mc N$: set $\mu^{\text{tr}}_{(i,j)}(-1) = 0$, $\forall j \in \mc N_i$. DNO: set $\lambda^{\text{mg}}(0)\!=\!0$, $\mu^{\text{tg}}(0) \!=\! 0$, $\mu_y^{\text{pb}}(0)\! = \!0$, $\forall y \!\in\! \mc B$.

@@

Some of the default cost parameters are set as in \cite{atzeni2013}, i.e., $Q_i^{\mathrm{di}}=0$, $c_i^{\mathrm{di}}=0.045\,  \text{\euro/kW}$, for all $i \in \mc N^{\mathrm{di}}$, $Q_i^{\mathrm{st}}=0$, $c_i^{\mathrm{st}}=0$, for all $i \in \mc N^{\mathrm{st}}$, and $d_h^{\mathrm{mg}}=0.1624/b_h \, \text{\euro/kW}$, whereas the trading cost parameters $c_{(i,j)}^{\mathrm{tr}}=0.08 \,  \text{\euro/kW}$, for all $(i,j) \in \mc E$, and $c^{\mathrm{ta}}=0.01 \,  \text{\euro/kW}$. The parameter $c_{(i,j)}^{\mathrm{tr}}$ is set larger than $c_i^{\mathrm{di}}$ to encourage trading between prosumers with and without dispatchable units, but is smaller than the average unit-price of importing power from the main grid. Note that, in some simulations, we vary these cost parameters. 
%
%
\subsection{Achieving operationally-safe solutions}
In the first simulation study, we compare the solutions obtained from solving a P2P market model with and without capacity constraints \eqref{eq:line_cap}. We specifically create an extreme case with $25$ prosumers, where the load of  prosumer $10$ (see Figure \ref{fig:simD_safe}) is very high. We solve both market designs using Algorithm~1. Figure \ref{fig:simD_safe} shows the resulting power-line saturations between busses for both designs. 
%
Some equilibrium solutions of the P2P market cause overcapacity in some lines when capacity constraints \eqref{eq:line_cap} are not taken into account in the model, as illustrated in Figure \ref{fig:simD_safe}~(b).
\begin{figure}[t]
	\centering
	\begin{subfigure}[t]{0.23\textwidth}
		\centering
		\includegraphics[scale=0.92]{figures/simD_safe1}
		\caption{With physical constraints}
	\end{subfigure}%
	~ 
	\begin{subfigure}[t]{0.27\textwidth}
		\centering
		\includegraphics[scale=0.92]{figures/simD_fail2}
		\caption{Without physical constraints}
	\end{subfigure}
	\caption{Power line capacities of the physical network. The solutions of the P2P market might cause overcapacity in some lines of the physical network when capacity constraints \eqref{eq:line_cap} are not taken into account.}
	\label{fig:simD_safe}
\end{figure}

@@

%	
\begin{figure}[htbp]
	\centering
	\includegraphics[width=.92\linewidth]{figures/b0a.eps}
	\caption{Total cost improvement (\euro) of each prosumer by trading ($c_{(i,j)}^{\mathrm{tr}}=0.08\text{\euro/kW}$).
	}
	\label{fig:simC_cost}
\end{figure}
%
\begin{figure}[htbp]
	\centering
	\includegraphics[width=.92\linewidth]{figures/b1a.eps}
	\caption{Aggregated P2P trading for different cost coefficients ($c_{(i,j)}^{\mathrm{tr}}$ in \euro/kW).
	}
	\label{fig:simC_ctr}
\end{figure}
%
\begin{figure}[t!]
	\centering
	\includegraphics[width=.92\linewidth]{figures/b2a.eps}
	\caption{Aggregated P2P trading for different penalty coefficients ($c^{\mathrm{ta}}$ in \euro/kW).
	}
	\label{fig:simC_pen}
\end{figure}
%
Then, we evaluate the sensitivity of the total traded power with respect to the trading cost parameter $c_{(i,j)}^{\mathrm{tr}}$ and the trading tariff, $c^{\mathrm{ta}}$. Figure \ref{fig:simC_ctr} shows that   $c_{(i,j)}^{\mathrm{tr}}$ must be set appropriately to maximize trading among prosumers. In other words, when $c_{(i,j)}^{\mathrm{tr}}$ is either too high or low, trading is less attractive. 
On the other hand, the higher the tariff is, the less power is traded, as shown in Figure \ref{fig:simC_pen}. Therefore, the DNO may adjust this tariff to encourage or discourage trading in the network. Discouraging trading might be needed when the capacity of the network is close to its limit.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{figures/simB_0402_pt1_v3a}
	\caption{	Incorporating storage units causes a peak-shaving effect on the sum of the total power imported from the main grid and the power locally generated.}
	\label{fig:sim_B1}
\end{figure}
\begin{figure}[t]
	\centering 
	%\hspace{-17pt}
	\includegraphics[width=0.92\linewidth]{figures/simB_0402_pt2_v4a}
	\caption{Aggregated P2P trading in scenarios (a) and (b).
	}
	\label{fig:sim_B2}
\end{figure}  
\begin{figure}[t]
	\centering 
	%\hspace{-17pt}
	\includegraphics[width=0.92\linewidth]{figures/simB_0402_pt3_v2a}
	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices.
	}
	\label{fig:sim_B3}
\end{figure}  
\iffalse 
\begin{figure}[!t]
	\centering
	\includegraphics[width=0.92\linewidth]{figures/simC_37_v2.eps}
	\caption{\textcolor{red}{[OLD]} Peak shaving effect with different per-unit cost of using storage.
	}
	\label{fig:simC}
\end{figure}
\fi 
%\clearpage

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{figures/simEF2.eps}
	\caption{Total number of iterations for convergence of Alg. 1 vs number of prosumers (top) and the connectivity level (the number of trading links) (bottom). {The average computation times of the inner loops, i.e., Algs.~2 and 3, obtained on a computer with Intel Xeon E5-2637 3.5 GHz processors and 128 GB of memory, are 74.5 ms and 1.13 s, respectively.} 
	}
	\label{fig:simE}
\end{figure}
